---
title: "NESDIS Five-Year Product Plan"
date: "September 2021"
output:
  word_document:
    reference_docx: "C:/Users/Elizabeth.Gugliotti/Documents/code/input/word-styles-reference-5YearPlan.docx"
    toc: true
    number_sections: true
    toc_depth: 4
---
```{r warning = FALSE, message = FALSE, echo = FALSE}
library(flexdashboard)
library(ggplot2)
library(scales)
library(shiny)
library(plyr)
library(dplyr)
library(tidyr)
library(plotly)
library(lubridate)
library(flextable)
library(pals)
source("C:/Users/Elizabeth.Gugliotti/Documents/code/TPIO/FlyoutTables/FlyoutDataCleanup.R")
```


```{r, warning = FALSE, message = FALSE, echo = FALSE}
#install_github("jeroenooms/jsonlite")
eores<-"https://eorestest.nesdis-hq.noaa.gov/ws/ws/"
#eores<-https://eoreswstest2.nesdis-hq.noaa.gov/ws/ws/"
#eores<-"https://eores.nesdis-hq.noaa.gov/ws/ws/"
#eores<-"https://eores.nesdis-hq.noaa.gov/ws/ws/"

#treename<-"EOA2016"
treename<-"NOSIA-II"
#treename<-"NOSIA-2-1"
#systems

r<-GET(paste0(eores,"get_reports_observing_system_basic_information",sep=""))
json_text<-content(r, as = "text")
systems_json<-fromJSON(json_text)
systems<-systems_json[['rptsystembasic']]

#platforms
r<-GET(paste0(eores,"get_reports_platform_basic_information",sep=""))
json_text<-content(r, as = "text")
platforms_json<-fromJSON(json_text)
platforms<-platforms_json[['rptpltfrmbasic']]

#platforms2system
r<-GET(paste0(eores,"get_reports_observing_system_platform_associations",sep=""))
json_text<-content(r, as = "text")
platform2system_json<-fromJSON(json_text)
platform2system<-platform2system_json[['rptsystem2pltfrm']]

#Sensing Elements
r<-GET(paste0(eores,"get_reports_sensing_element_basic_information",sep=""))
json_text<-content(r, as = "text")
se_json<-fromJSON(json_text)
se<-se_json[['rptsebasic']]

#se2platform
r<-GET(paste0(eores,"get_reports_platform_sensing_element_associations",sep=""))
json_text<-content(r, as = "text")
se2platform_json<-fromJSON(json_text)
se2platform<-se2platform_json[['rptpltfrm2se']]

#environmental parameters
r<-GET(paste0(eores,"get_reports_environmental_parameter_basic_information",sep=""))
json_text<-content(r, as = "text")
ep_json<-fromJSON(json_text)
ep<-ep_json[['rptenvparambasic']]

#se2ep
r<-GET(paste0(eores,"get_reports_sensing_element_environmental_parameter_associations",sep=""))
json_text<-content(r, as = "text")
ep2se_json<-fromJSON(json_text)
ep2se<-ep2se_json[['rptse2envparam']]

#platform dates
r<-GET(paste0(eores,"get_reports_platform_key_dates",sep=""))
json_text<-content(r, as = "text")
platform2dates_json<-fromJSON(json_text)
platform2dates<-platform2dates_json[['rptpltfrmdates']]
```

```{r, warning = FALSE, echo = FALSE}
system_joins <- systems %>%
  left_join(platform2system, by = "system_id") %>%
  left_join(platforms, by = "platform_id") %>%
  left_join(platform2dates, by = "platform_id") %>%
  left_join(se2platform, by = "platform_id") %>%
  left_join(se, by = "sensing_element_id") %>%
  left_join(ep2se, by = "sensing_element_id") %>%
  left_join(ep, by = "environmental_parameter_id") %>% 
  filter(grepl("Baseline Product", environmental_parameter_name)) %>% 
  filter(date_type %in% c("Date End of Life (EOL)", "Date Launched", NA)) %>%
  mutate(Orbit = ifelse(orbit_type == "Sun-synchronous", paste0(orbit_type," (",orbit_crossing_time," ",
                        sun_side_equatorial_crossing_mode,")"),
                        ifelse(orbit_type =="Geostationary", paste0(orbit_type," (",
                               satellite_longitude_deg,")"),
                               ifelse(orbit_type == "Drifting", paste0(orbit_type," (",
                                      orbit_inclination_deg,")"), orbit_type)))) %>%
  separate(environmental_parameter_name, c("Baseline_Product", "extra"), extra = "drop", sep = " Baseline Product") %>%
  separate(sensing_element_name, c("sensing_element_name", "extra"), extra = "drop", sep = " Product") %>%
  select(platform_name, platform_acronym, Orbit, date_type, date, sensing_element_name, sensing_element_acronym, Baseline_Product, geographic_coverage) %>%
  distinct(platform_name, platform_acronym, sensing_element_name, sensing_element_acronym, Baseline_Product, date_type, geographic_coverage, .keep_all = TRUE) %>% 
  pivot_wider(names_from = date_type, values_from = date) %>% select(-`NA`)
```


# Introduction



# Planned Data Sources
Table 2-2 NESDIS Data Sources
```{r, warning = FALSE, echo = FALSE}
# Table
# | NOAA Satellite Data | Non-NOAA Satellite Data | Exploitation Data Sources |

still_flying_NOAA<- flyout_clean %>%
  pivot_wider(names_from = date_type, values_from = date) %>% 
  select(system_name:`Date Launched`) %>%
  filter(osc_baseline_observing_system_category == "Critical") %>%
  mutate(`Date End of Life (EOL)` = as.numeric(year(`Date End of Life (EOL)`))) %>%
  mutate(`Date Launched` = as.numeric(year(`Date Launched`))) %>% 
#  filter(`Date End of Life (EOL)` >= year(Sys.Date())) %>%
  filter(`Date Launched` <= 2027| is.na(`Date Launched`)) %>% 
  filter(!platform_life_cycle_phase %in% c("Failed", "Retired")) %>% 
  filter(owner_name %in% c("National Oceanic and Atmospheric Administration (NOAA)", NA)) %>% 
  distinct(platform_name, .keep_all = TRUE)

still_flying_non_NOAA<- flyout_clean %>%
  pivot_wider(names_from = date_type, values_from = date) %>% 
  select(system_name:`Date Launched`) %>%
  filter(osc_baseline_observing_system_category == "Critical") %>%
  mutate(`Date End of Life (EOL)` = as.numeric(year(`Date End of Life (EOL)`))) %>%
  mutate(`Date Launched` = as.numeric(year(`Date Launched`))) %>% 
#  filter(`Date End of Life (EOL)` >= year(Sys.Date())) %>%
  filter(`Date Launched` <= 2027| is.na(`Date Launched`)) %>% 
  filter(!platform_life_cycle_phase %in% c("Failed", "Retired")) %>% 
  filter(!platform_acronym %in% still_flying_NOAA$platform_acronym) %>% 
  distinct(platform_name, .keep_all = TRUE)


still_flying_data_exp<- flyout_clean %>%
  pivot_wider(names_from = date_type, values_from = date) %>% 
  select(system_name:`Date Launched`) %>%
  filter(system_intended_use == "Research") %>%
  filter(!is.na(osc_baseline_observing_system_category)) %>%
  mutate(`Date End of Life (EOL)` = as.numeric(year(`Date End of Life (EOL)`))) %>%
  mutate(`Date Launched` = as.numeric(year(`Date Launched`))) %>% 
#  filter(`Date End of Life (EOL)` >= year(Sys.Date())) %>%
  filter(`Date Launched` <= 2027| is.na(`Date Launched`)) %>% 
  filter(!platform_life_cycle_phase %in% c("Failed", "Retired")) %>% 
  filter(!platform_acronym %in% still_flying_NOAA$platform_acronym) %>% 
  distinct(platform_name, .keep_all = TRUE)
```

```{r, warning = FALSE, echo = FALSE}
# Product Function
by_product<- function(dat, product){
  
dat1 <- dat %>% 
  dplyr::filter(Baseline_Product == product) %>% 
  dplyr::distinct(platform_name, platform_acronym, sensing_element_name, sensing_element_acronym, Baseline_Product,`Date End of Life (EOL)`, `Date Launched`, .keep_all = TRUE) %>% 
  dplyr::mutate(platform_sensor = paste0(platform_acronym," ", sensing_element_acronym)) %>%
  dplyr::select(platform_sensor, Orbit, `Date End of Life (EOL)`, `Date Launched`) %>%
  dplyr::filter(!is.na(`Date Launched`)) %>%
  dplyr::filter(!is.na(`Date End of Life (EOL)`))%>%
  dplyr::mutate(`Date Launched` = as.Date(`Date Launched`, "%m-%d-%Y")) %>%
  dplyr::mutate(`Date End of Life (EOL)` = as.Date(`Date End of Life (EOL)`, "%m-%d-%Y"))

M <- Map(seq, dat1$`Date Launched`, dat1$`Date End of Life (EOL)`, by = "year")

dat2 <- data.frame(
    platform_sensor = rep.int(dat1$platform_sensor, vapply(M, length, 1L)),
    Orbit = rep.int(dat1$Orbit, vapply(M, length, 1L)),
    Year = as.Date(do.call(c, M), format = "%m-%d-%Y"))

dat_wide<- dat2 %>%
    filter(Year >= "2019-01-01" & Year <= "2027-12-31") %>%
    dplyr::mutate(flying = "YES") %>%
    dplyr::arrange(Year) %>%
    dplyr::mutate(Year = year(Year)) %>%
    dplyr::mutate(Orbit = ifelse(is.na(Orbit), "TBD", Orbit)) %>%
    pivot_wider(names_from = Year, values_from = flying) %>% 
    as.data.frame() %>% 
    dplyr::arrange(platform_sensor) %>%
    dplyr::rename(` ` = platform_sensor)}
```

# Foundational

## Imagery
### Visible and IR Imagery
#### LEO Imagery
```{r, warning = FALSE, echo = FALSE}
#Filter for when orbit == sun-synchronous
```
#### GEO Imagery
```{r, warning = FALSE, echo = FALSE}
#Filter for when orbit == geostationary
```
#### Arctic Composite
```{r, warning = FALSE, echo = FALSE}
#Filter for when geographic coverage == arctic
```
#### Global Mosaic of Vis/IR Imagery
```{r, warning = FALSE, echo = FALSE}
#????
```
#### CoastWatch/OceanWatch Imagery, Biology, Biogeochemistry
```{r, warning = FALSE, echo = FALSE}
#????
```

### Microwave Sounder Imagery
#### Limb Corrected ATMS Imagery
```{r, warning = FALSE, echo = FALSE}
#????
```

### Microwave Imager Imagery - See Ocean Wind GAASP
### Near Constant Contrast - See Visible and IR Imagery - LEO Imagery
### SAR Imagery
#### Synthetic Aperture Radar (SAR) Automated Ocean Products System (SAROPS)
```{r, warning = FALSE, echo = FALSE}
# Maybe filter by products that belong to SAR Sensors???
```


## Sensor Data
### Microwave Radiometer Brightnesss Temperatures
```{r, warning = FALSE, echo = FALSE}
#Filter for sensor data & brightness temperature data?
```

### Microwave Radiometer Raw Data Records
### Microwave Radiometer Temperature Data Records
### Microwave Radiometer Sensor Data Records
### Infrared Sounder Cloud-Cleared Radiances - See Atmospheric Temperature HEAPS
### Infrared Sounder Radiances
### Infrared Sounder Principal Components/Thinned Radiances
### Infrared Sounder All-Sky Radiances
### Infrared Sounder Clear-Sky Radiances
### Infrared Sounder Raw Data Records
### Infrared Sounder Sensor Data Records
### Shortwave (UV/VIS) Sounder Raw Data Records
### Shortwave (UV/VIS) Sounder Sensor Data Records
### Shortwave (UV/VIS) Sounder Sensor Reflectance
### Optical Imager Raw Data
### Optical Imager Reflectance
### Optical Imager Radiance
### Optical Imager Brightness Temperature
### Lightning Imager
### Scatterometers
### Radar and LIDAR Altimeter
### Radio Occultation


# Geophysical
## Atmosphere
### Atmospheric Composition and Air Quality
#### Aerosol Optical Depth and Thickness
```{r warning = FALSE, echo = FALSE}
yo<-by_product(system_joins, "Aerosol Optical Depth/Thickness")
yo<-yo %>%
    flextable()%>%
    width(width = 1) %>%
    color(j = 3:ncol(yo), color = "slateblue") %>%
    bg(j = 3:ncol(yo), bg = "slateblue") %>%
    bold(part = "header") %>%
    bold(j = 1)%>% autofit()
yo
```
#### Aerosol Particle Properties
```{r warning = FALSE, echo = FALSE, eval = FALSE}
yo<-by_product(system_joins, "Aerosol Particle Properties")
yo<-yo %>%
    flextable()%>%
    width(width = 1) %>%
    color(j = 3:ncol(yo), color = "slateblue") %>%
    bg(j = 3:ncol(yo), bg = "slateblue") %>%
    bold(part = "header") %>%
    bold(j = 1)%>% autofit()
yo
```
#### Aerosol Detection
```{r, warning = FALSE, echo = FALSE}
yo<-by_product(system_joins, "Aerosol Detection")
yo<- yo %>%
    flextable()%>%
    width(width = 1) %>%
    color(j = 3:ncol(yo), color = "slateblue") %>%
    bg(j = 3:ncol(yo), bg = "slateblue") %>%
    bold(part = "header") %>%
    bold(j = 1)%>% autofit()
yo
```
#### Biomass Burning Emissions
```{r, warning = FALSE, echo = FALSE}
yo<-by_product(system_joins, "Biomass Burning Emissions")
yo <- yo %>%
    flextable()%>%
    width(width = 1) %>%
    color(j = 3:ncol(yo), color = "slateblue") %>%
    bg(j = 3:ncol(yo), bg = "slateblue") %>%
    bold(part = "header") %>%
    bold(j = 1)%>% autofit()
yo
```
#### Total Ozone
```{r, warning = FALSE, echo = FALSE}
yo<-by_product(system_joins, "Total Ozone")
yo <- yo %>%
    flextable()%>%
    width(width = 1) %>%
    color(j = 3:ncol(yo), color = "slateblue") %>%
    bg(j = 3:ncol(yo), bg = "slateblue") %>%
    bold(part = "header") %>%
    bold(j = 1)%>% autofit()
yo
```
#### Ozone Profile
```{r, warning = FALSE, echo = FALSE}
yo<-by_product(system_joins, "Ozone Profile")
yo <- yo %>%
    flextable()%>%
    width(width = 1) %>%
    color(j = 3:ncol(yo), color = "slateblue") %>%
    bg(j = 3:ncol(yo), bg = "slateblue") %>%
    bold(part = "header") %>%
    bold(j = 1)%>% autofit()
yo
```
#### Trace Gases Product Suite
```{r, warning = FALSE, echo = FALSE}
yo<-by_product(system_joins, "Trace Gases Product Suite")
yo <- yo %>%
    flextable()%>%
    width(width = 1) %>%
    color(j = 3:ncol(yo), color = "slateblue") %>%
    bg(j = 3:ncol(yo), bg = "slateblue") %>%
    bold(part = "header") %>%
    bold(j = 1)%>% autofit()
yo
```


### Atmospheric Water Vapor
### Atmospheric Temperature
### Clouds
### Lightning
### Precipitation
### Radiation Budget
### Tropical Cyclone Characteristics
### Winds

## Cryosphere
### Lake and Sea Ice
### Snow and Glacier

## Land and Surface Hydrology
### Fires
### Floods
### Surface Moisture
### Surface Temperature
### Vegetation

## Oceans, Freshwater and Coasts
### Surface Height
#### Sea Surface Height
```{r, warning = FALSE, echo = FALSE}
yo<-by_product(system_joins, "Sea Surface Height")
yo <- yo %>%
    flextable()%>%
    width(width = 1) %>%
    color(j = 3:ncol(yo), color = "slateblue") %>%
    bg(j = 3:ncol(yo), bg = "slateblue") %>%
    bold(part = "header") %>%
    bold(j = 1)%>% autofit()
yo
```


### Bathymetry
### Water Temperature and Salinity
### Biology and Biogeochemistry
### Water Pollution

## Space Weather
### Heliosphere
### Ionosphere
### Magnetosphere
### Solar


# Analytical
## Weather
### Automated Severe Weather Analyses and Nowcasts

## Climate
### Climate Data Records

## Oceans, Freshwater and Coasts


#### Appendix A: Budget Planning and Funding Strategy {.unnumbered}

#### Appendix B: Acronyms {.unnumbered}

#### Appendix C: Product Prioritization Methodology {.unnumbered}


```{r}

```


```{r}

```



```{r pressure, echo=FALSE}
plot(pressure)
```

